---
title: "New house"
author: "Priyanka Mohekar"
date: "11 July 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
train <- read.csv("E://Machine Learning/Practice/House Price Advanced regression techniques/train.csv")

test_data <- read.csv("E://Machine Learning/Practice/House Price Advanced regression techniques/test.csv")

actual <- read.csv("E://Machine Learning/Practice/House Price Advanced regression techniques/sample_submission.csv")
```

```{r}
summary(train)
```

```{r}
change_char_to_factor <- function(df){
    for(col in names(df)){
        if(class(df[, col]) == "character" ){
            if(sum(is.na(df[,col])) == 0 ){
                df[, col] <- as.factor(df[, col])
            } else {
                df[, col] <- NULL
            }
        }
    }
    return (df)
}

pre_process <- function(df, method){
    pre_model <- preProcess(df, method = method) 
    pre_data <- predict(pre_model, df)
    
    return (pre_data)
}

evalute_model <- function(model, data, y){
    prediction <- predict(model, data)
    pred_df <- data.frame(obs = y, pred=prediction)
    return (pred_df)
}
```



```{r}
sum(is.na(train))

#Data cleansing
sum(is.na(train$Alley))

train$Alley <- NULL
    
sum(is.na(train$PoolQC))

train$PoolQC <- NULL
    
sum(is.na(train$Fence))

train$Fence <- NULL
    
sum(is.na(train$MiscFeature))

train$MiscFeature <- NULL
    
train$Id<- NULL
    
train_clean <- change_char_to_factor(train)
    
#glimpse(train_clean)
```

```{r}
sum(is.na(train))
```

```{r}
set.seed(42)
rows <- sample(nrow((train_clean)))
training <- train_clean[rows,]
split <- round(nrow(train_clean)*.80)
train_data <- training[1:split, ]
test_data <- training[(split + 1):nrow(training), ]
nrow(train_data) + nrow(test_data)
```
Data preprocessing
```{r}
x_train <- train_data[-ncol(train_data)]
y_train <- train_data %>% select(SalePrice)
x_test <- test_data[-ncol(test_data)]
y_test <- test_data %>% select(SalePrice)
```

Data preprocessing - Median imputation
```{r}
library(caret)
x_train_mi <- pre_process(x_train, "medianImpute")
x_test_mi <- pre_process(x_test, "medianImpute")
train_mi <- x_train_mi %>% mutate(SalePrice = train_data[, ncol(train_data)])
test_mi <- x_test_mi %>% mutate(SalePrice = test_data[, ncol(test_data)])
#glimpse(train_mi)
```
### Data preprocessing - Median imputation, Centering and Scaling 
```{r comment=FALSE}
x_train_mcs <- pre_process(x_train, c("medianImpute", "center", "scale"))
x_test_mcs <- pre_process(x_test, c("medianImpute", "center", "scale"))
train_mcs <- x_train_mcs %>% mutate(SalePrice = train_data[, ncol(train_data)])
test_mcs <- x_test_mcs %>% mutate(SalePrice = test_data[, ncol(test_data)])
#glimpse(train_mcs)
#glimpse(test_mcs)
nrow(test_mcs) + nrow(train_mcs)
```
### Data preprocessing - knn
```{r}
library(RANN)
x_train_knn <- pre_process(x_train,"knnImpute")
x_test_knn <- pre_process(x_test, "knnImpute")
train_knn <- x_train_knn %>% mutate(SalePrice = train_data[, ncol(train_data)])
test_knn <- x_test_knn %>% mutate(SalePrice = test_data[, ncol(test_data)])
#glimpse(train_knn)
#glimpse(test_knn)
nrow(test_knn) + nrow(train_knn)
```

## Modelling
### Train Control with 5X5 folds cross validation
```{r }
library(caret)
myControl <- trainControl(method="repeatedcv", number = 5, repeats = 5, verboseIter = TRUE)
```

### Linear Model
#### Linear Model with data preprocessed using Median imputation 
```{r, message=F, warning=F}
model_lm_mi <- caret::train( SalePrice ~ ., data = (train_mi %>% select(-MasVnrType,-BsmtQual,-BsmtCond,-BsmtExposure,-BsmtFinType1,-GarageQual,-GarageCond,-GarageFinish,-FireplaceQu,-GarageType,-Electrical,-BsmtFinType2)), method="lm",
                trControl = myControl)
model_lm_mi
```
#### Linear Model with data preprocessed using Median imputation, Centering and Scaling
```{r, message=F, warning=F}
model_lm_mcs <- caret::train( SalePrice ~ ., data = (train_mcs%>% select(-MasVnrType,-BsmtQual,-BsmtCond,-BsmtExposure,-BsmtFinType1,-GarageQual,-GarageCond,-GarageFinish,-FireplaceQu,-GarageType,-Electrical,-BsmtFinType2)), method="lm",
                trControl = myControl)
model_lm_mcs
```
#### Linear Model with data preprocessed using knn
```{r, message=F, warning=F}
model_lm_knn <- caret::train( SalePrice ~ ., data = (train_knn%>% select(-MasVnrType,-BsmtQual,-BsmtCond,-BsmtExposure,-BsmtFinType1,-GarageQual,-GarageCond,-GarageFinish,-FireplaceQu,-GarageType,-Electrical,-BsmtFinType2)), method="lm",
                trControl = myControl)model_lm_knn
```
#### Compare the three models using the RMSE
```{r} 
lm_list <- list(lm_mi = model_lm_mi, lm_mcs = model_lm_mcs, lm_knn = model_lm_knn)
resamples <- resamples(lm_list)
summary(resamples)
bwplot(resamples, metric="RMSE")
```
### Generalized Linear Model
#### Generalized Linear Model with data preprocessed using Median imputation
```{r, message=F, warning=F}
  model_glm_mi <- caret::train( SalePrice ~ ., data = (train_mi%>% select(-MasVnrType,-BsmtQual,-BsmtCond,-BsmtExposure,-BsmtFinType1,-GarageQual,-GarageCond,-GarageFinish,-FireplaceQu,-GarageType,-Electrical,-BsmtFinType2)), method="glm",
                trControl = myControl)
    model_glm_mi
```
#### Generalized Linear Model with data preprocessed using Median imputation, Centering and Scaling 
```{r, message=F, warning=F}
model_glm_mcs <- caret::train( SalePrice ~ ., data = (train_mcs%>% select(-MasVnrType,-BsmtQual,-BsmtCond,-BsmtExposure,-BsmtFinType1,-GarageQual,-GarageCond,-GarageFinish,-FireplaceQu,-GarageType,-Electrical,-BsmtFinType2)), method="glm",
                trControl = myControl)
model_glm_mcs
```
#### Generalized Linear Model with data preprocessed using knn
```{r, message=F, warning=F}
model_glm_knn <- caret::train( SalePrice ~ ., data = (train_knn%>% select(-MasVnrType,-BsmtQual,-BsmtCond,-BsmtExposure,-BsmtFinType1,-GarageQual,-GarageCond,-GarageFinish,-FireplaceQu,-GarageType,-Electrical,-BsmtFinType2)), method="glm",
                trControl = myControl)
model_glm_knn
```
#### Compare the three models using the RMSE
```{r} 
  glm_list <- list(glm_mi = model_glm_mi, glm_mcs = model_glm_mcs, glm_knn = model_glm_knn)
  resamples <- resamples(glm_list)
  summary(resamples)
  bwplot(resamples, metric="RMSE")
```

### Gmlnet Model
#### Glmnet with data preprocessed using Median imputation 
```{r, message=F, warning=F}
  model_glmnet_mi <- caret::train( SalePrice ~ ., data =(train_mi%>% select(-MasVnrType,-BsmtQual,-BsmtCond,-BsmtExposure,-BsmtFinType1,-GarageQual,-GarageCond,-GarageFinish,-FireplaceQu,-GarageType,-Electrical,-BsmtFinType2)), metric="RMSE", method="glmnet", tuneGrid = expand.grid(alpha = 0.1, lambda = 0:10/10),
                       trControl = myControl)
    model_glmnet_mi
```
#### Glmnet with data preprocessed using Median imputation, Centering and Scaling method
```{r, message=F, warning=F}
 model_glmnet_mcs <- caret::train( SalePrice ~ ., data = (train_mcs%>% select(-MasVnrType,-BsmtQual,-BsmtCond,-BsmtExposure,-BsmtFinType1,-GarageQual,-GarageCond,-GarageFinish,-FireplaceQu,-GarageType,-Electrical,-BsmtFinType2)), metric="RMSE", method="glmnet", tuneGrid = expand.grid(alpha = 0.1, lambda = 0:10/10),
                       trControl = myControl)
    model_glmnet_mcs
```
#### Glmnet with data preprocessed using knn method
```{r, message=F, warning=F}
  model_glmnet_knn <- caret::train( SalePrice ~ ., data = (train_mcs%>% select(-MasVnrType,-BsmtQual,-BsmtCond,-BsmtExposure,-BsmtFinType1,-GarageQual,-GarageCond,-GarageFinish,-FireplaceQu,-GarageType,-Electrical,-BsmtFinType2)), metric="RMSE", method="glmnet", tuneGrid = expand.grid(alpha = 0.1, lambda = 0:10/10),
                       trControl = myControl)
    model_glmnet_knn
```
#### Compare the three models using the RMSE
```{r} 
  glmnet_list <- list(glmnet_mi = model_glmnet_mi, glmnet_mcs = model_glmnet_mcs, glmnet_knn = model_glmnet_knn)
  resamples <- resamples(glmnet_list)
  summary(resamples)
  bwplot(resamples, metric="RMSE")
```
### Random forest
#### Random Forest with data preprocessed using Median imputation 
```{r, message=F, warning=F}
  model_rf_mi <- caret::train( SalePrice ~ ., data = train_mi%>% select(-MasVnrType,-BsmtQual,-BsmtCond,-BsmtExposure,-BsmtFinType1,-GarageQual,-GarageCond,-GarageFinish,-FireplaceQu,-GarageType,-Electrical,-BsmtFinType2), method="ranger",
                trControl = myControl)
    model_rf_mi
```
#### Random Forest with data preprocessed using Median imputation, Centering and Scaling 
```{r, message=F, warning=F}
  model_rf_mcs <- caret::train( SalePrice ~ ., data = train_mcs%>% select(-MasVnrType,-BsmtQual,-BsmtCond,-BsmtExposure,-BsmtFinType1,-GarageQual,-GarageCond,-GarageFinish,-FireplaceQu,-GarageType,-Electrical,-BsmtFinType2), method="ranger",
                trControl = myControl)
model_rf_mcs
```
#### Random Forest with data preprocessed using knn
```{r, message=F, warning=F}
  model_rf_knn <- caret::train( SalePrice ~ ., data = train_knn%>% select(-MasVnrType,-BsmtQual,-BsmtCond,-BsmtExposure,-BsmtFinType1,-GarageQual,-GarageCond,-GarageFinish,-FireplaceQu,-GarageType,-Electrical,-BsmtFinType2), method="ranger",
                trControl = myControl)
    model_rf_knn
```

#### Compare the three models using the RMSE
```{r} 
  rf_list <- list(rf_mi = model_rf_mi, rf_mcs = model_rf_mcs, rf_knn = model_rf_knn)
  resamples <- resamples(rf_list)
  summary(resamples)
  bwplot(resamples, metric="RMSE")
```

## Compare all the models
```{r} 
 all_list <- append(append(append(lm_list, glm_list), glmnet_list), rf_list)
 all_list
 resamples <- resamples(all_list)
 summary(resamples)
 bwplot(resamples, metric="RMSE")
```

## Evaluate the Models on test data
### Linear Models
#### Linear Model with data preprocessed using Median imputation
```{r warning=FALSE} 
  pred_df_lm_mi <- evalute_model(model_lm_mi, test_mi, test_mi$SalePrice)
  defaultSummary(pred_df_lm_mi)
  xyplot(pred_df_lm_mi$obs ~ pred_df_lm_mi$pred, type = c("p", "g"), xlab = "Predicted", ylab = "Observed")
  
```

#### Linear Model with data preprocessed using Median imputation, Centering and Scaling method
```{r, message=F, warning=F}
  pred_df_lm_mcs <- evalute_model(model_lm_mcs, test_mcs, test_mcs$SalePrice)
  defaultSummary(pred_df_lm_mcs)
  xyplot(pred_df_lm_mcs$obs ~ pred_df_lm_mcs$pred, type = c("p", "g"), xlab = "Predicted", ylab = "Observed")
```

#### Linear Model with data preprocessed using knn
```{r, message=F, warning=F}
  pred_df_lm_knn <- evalute_model(model_lm_knn, test_knn, test_knn$SalePrice)
  defaultSummary(pred_df_lm_knn)
  xyplot(pred_df_lm_knn$obs ~ pred_df_lm_knn$pred, type = c("p", "g"), xlab = "Predicted", ylab = "Observed")
```

### Generalized Linear Models
#### Generalized Linear Model with data preprocessed using Median imputation 
```{r warning=FALSE} 
  pred_df_glm_mi <- evalute_model(model_glm_mi, test_mi, test_mi$SalePrice)
  head(pred_df_glm_mi)
  defaultSummary(pred_df_glm_mi)
  xyplot(pred_df_glm_mi$obs ~ pred_df_glm_mi$pred, type = c("p", "g"), xlab = "Predicted", ylab = "Observed")
```

#### Generalized Linear Model with data preprocessed using Median imputation, Centering and Scaling
```{r, message=F, warning=F}
  pred_df_glm_mcs <- evalute_model(model_glm_mcs, test_mcs, test_mcs$SalePrice)
  head(pred_df_glm_mcs)
  defaultSummary(pred_df_glm_mcs)
  xyplot(pred_df_glm_mcs$obs ~ pred_df_glm_mcs$pred, type = c("p", "g"), xlab = "Predicted", ylab = "Observed")
```

#### Generalized Linear Model with data preprocessed using knn
```{r, message=F, warning=F}
  pred_df_glm_knn <- evalute_model(model_glm_knn, test_knn, test_knn$SalePrice)
  head(pred_df_glm_knn)
  defaultSummary(pred_df_glm_knn)
  xyplot(pred_df_glm_knn$obs ~ pred_df_glm_knn$pred, type = c("p", "g"), xlab = "Predicted", ylab = "Observed")
```

### Glmnet Models
#### Glmnet Model with data preprocessed using Median imputation 
```{r warning=FALSE} 
  pred_df_glmnet_mi <- evalute_model(model_glmnet_mi, test_mi, test_mi$SalePrice)
  head(pred_df_glmnet_mi)
  defaultSummary(pred_df_glmnet_mi)
  xyplot(pred_df_glmnet_mi$obs ~ pred_df_glmnet_mi$pred, type = c("p", "g"), xlab = "Predicted", ylab = "Observed")
 
```

#### Glmnet Model with data preprocessed using Median imputation, Centering and Scaling
```{r, message=F, warning=F}
  pred_df_glmnet_mcs <- evalute_model(model_glmnet_mcs, test_mcs, test_mcs$SalePrice)
  head(pred_df_glmnet_mcs)
  defaultSummary(pred_df_glmnet_mcs)
  xyplot(pred_df_glmnet_mcs$obs ~ pred_df_glmnet_mcs$pred, type = c("p", "g"), xlab = "Predicted", ylab = "Observed")
```

#### Glmnet Linear Model with data preprocessed using knn
```{r, message=F, warning=F}
  pred_df_glmnet_knn <- evalute_model(model_glmnet_knn, test_knn, test_knn$SalePrice)
  head(pred_df_glmnet_knn)
  defaultSummary(pred_df_glmnet_knn)
  xyplot(pred_df_glmnet_knn$obs ~ pred_df_glmnet_knn$pred, type = c("p", "g"), xlab = "Predicted", ylab = "Observed")
```

### Random Forest
#### Random Forest with data preprocessed using Median imputation method
```{r warning=FALSE} 
  pred_df_rf_mi <- evalute_model(model_rf_mi, test_mi, test_mi$SalePrice)
  defaultSummary(pred_df_rf_mi)
  head(pred_df_rf_mi)
  xyplot(pred_df_rf_mi$obs ~ pred_df_rf_mi$pred, type = c("p", "g"), xlab = "Predicted", ylab = "Observed")
```

#### Random Forest with data preprocessed using Median imputation, Centering and Scaling
```{r, message=F, warning=F}
  pred_df_rf_mcs <- evalute_model(model_rf_mcs, test_mcs, test_mcs$SalePrice)
  head(pred_df_rf_mcs)
  defaultSummary(pred_df_rf_mcs)
  xyplot(pred_df_rf_mcs$obs ~ pred_df_rf_mcs$pred, type = c("p", "g"), xlab = "Predicted", ylab = "Observed")
```

#### Random Forest with data preprocessed using KNN method
```{r, message=F, warning=F}
  pred_df_rf_knn <- evalute_model(model_rf_knn, test_knn, test_knn$SalePrice)
  head(pred_df_rf_knn)
  defaultSummary(pred_df_rf_knn)
  xyplot(pred_df_rf_knn$obs ~ pred_df_rf_knn$pred, type = c("p", "g"), xlab = "Predicted", ylab = "Observed")
```